 \documentclass[12pt]{article}

\usepackage[margin=0.7in]{geometry}
\usepackage{color,colordvi,pxfonts,marvosym,revnum,textcomp}

%\usepackage{amsmath}
\usepackage{enumitem}

\setlength{\parindent}{0em}
\setlength{\parskip}{1ex plus0.5ex minus0.2ex} 

\setlength{\fboxsep}{2.5pt}

\newcommand{\mine}{
  \addtocounter{enumi}{1}
\item[\fcolorbox{white}{grey}{\color{white} \tiny \arabic{enumi}}]
}

\definecolor{grey}{gray}{0.35}

\newcommand{\dg}[1]{{\color{black} $\blacktriangleright$ {#1}}}
\newcommand{\dn}[1]{{\color{black} {#1}}}

\newcommand{\mybll}[1]{\smallskip\begin{enumerate}[start=1,label={},leftmargin=\parindent]\setlength{\itemsep}{#1}\vspace*{-0.7em}}
\newcommand{\myben}[1]{\smallskip\begin{enumerate}[start=1,label={\scriptsize \arabic*$\ $},leftmargin=\parindent]\setlength{\itemsep}{#1}\vspace*{-0.7em}}
\newcommand{\mycon}[1]{\smallskip\begin{enumerate}[resume,label={\scriptsize \arabic*$\ $},leftmargin=\parindent]\setlength{\itemsep}{#1}\vspace*{-0.7em}}
\newcommand{\mydot}[1]{\begin{enumerate}[label=$\circ$,leftmargin=\parindent]\setlength{\itemsep}{#1}}
\newcommand{\ee}{\end{enumerate}}

\newcommand{\mytitle}[1]{\subsection*{#1}\smallskip}

\newcommand{\mylift}[1]{\vspace*{#1}}

\begin{document}

\hfill \today

\begin{center}
{\bf CURRICULUM VITAE}\\
Abhirup Datta\\[3mm]
\end{center}

%\vspace*{10mm}

%\subsection*{PROFESSIONAL DATA}

\textbf{Address:} Department of Biostatistics, Johns Hopkins Bloomberg School of Public Health.\\[0.2em]
615 North Wolfe Street, \#E3640, Baltimore, MD 21205.

\textbf{Phone:} (410) 502 2988  
\hfill \textbf{Email:} abhidatta@jhu.edu 
%\textbf{Webpage:} abhidatta.com 
%\textbf{Github:} https://github.com/abhirupdatta
%\textbf{Twitter:} @dattascience
\mylift{-1.5em}
\subsection*{Education}

%\subsection*{Degrees}

%\mydot{-0.1em}

\mylift{-.5em}\begin{tabular}{lll}
\textbf{Degree} & \textbf{Year} & \textbf{Institution}\\
PhD, Biostatistics & 2016 & University of Minnesota, Twin Cities, MN\\
MStat & 2010 & Indian Statistical Institute, Kolkata, India\\
(Specialization in Math-Stat-Probability) & &  \\
BStat (with Honors) & 2008 & Indian Statistical Institute, Kolkata, India,
%\item BStat (Hons.), Indian Statistical Institute, Kolkata, India (2008).
\end{tabular}

%\ee

\mylift{-1.em}

\subsection*{Professional Experience}
\mydot{-0.1em}
\item \vskip -3mm
2016 -- present: Assistant Professor, Department of Biostatistics, Johns Hopkins University.
%\item 2017 -- present: Affiliate Faculty, The Spatial Science for Public Health Center, Johns Hopkins University.
\item 2010 -- 2012: Quantitative analyst, Morgan Stanley.
\ee
%\subsection*{PROFESSIONAL ACTIVITIES}
%\smallskip
\mylift{-2.5em}
\subsection*{Professional Memberships}
\vskip -3mm American Statistical Association,  International Biometric Society (Eastern North American Region (ENAR)), International Indian Statistical Association (IISA), The International Environmetric Society (TIES) of the International Statistical Institute (ISI) 

\mylift{-1.5em}
%\subsection*{Program Development}
%
%\mydot{-0.1em}
%\item Student paper award reviewer, Section on Bayesian Statistical Science, Joint Statistical Meetings (2021).
%\item Grant review-panel National Science Foundation (NSF) Division of Mathematical Sciences (DMS) (2020)
%\item Scientific Program Committee for the International Indian Statistical Association conference (IISA) (2021).
%\item Session Chair, Joint Statistical Meetings (2020).
%\item Student poster competition judge, International Indian Statistical Association (IISA) INDSTAT conference (2019).
%\item Session Chair, International Indian Statistical Association (IISA) INDSTAT conference (2019).
%\item Session Chair, Joint Statistical Meetings (2019).
%\item Session Organizer, Joint Statistical Meetings (2019).
%\item Student paper award reviewer, Section on Bayesian Statistical Science, Joint Statistical Meetings (2019).
%\item Session Organizer, Joint Statistical Meetings (2018).
%\item Student paper award reviewer, Section on Bayesian Statistical Science, Joint Statistical Meetings (2018).
%\item Session Chair, Joint Statistical Meetings (2014).
%\ee
%

%\subsection*{EDITORIAL ACTIVITIES}
%\smallskip
\subsection*{Editorial Board} \vskip -3mm 2020 - \quad \quad Journal of Computation and Graphical Statistics
\mylift{-1.5em}
\subsection*{Peer Review Activities \ {\small \em  The numbers of manuscripts reviewed exclude revisions.}} \vskip -3mm
Advances in Statistical Climatology Meteorology and Oceanography (1), Annals of Applied Statistics (5), Bayesian Analysis (1), Biometrics (4), Biometrika (1), Computational Statistics and Data Analysis (CSDA) (3), Electronic Journal of Statistics (1), Environmental Science and Technology (ES\&T) (1), Environmetrics (2), Harvard Data Science Review (1), IEEE Transactions on Pattern Analysis and Machine Intelligence (1), Journal of Agricultural Biological and Environmental Statistics (JABES) (1), Journal of the American Statistical Association Applications and Case Studies (JASA-ACS) (3), Journal of the American Statistical Association Theory and Methods (JASA-TM) (8), Journal of Computation and Graphical Statistics (JCGS) (4), Journal of Multivariate Analysis (JMVA) (1), Journal of the Royal Statistical Society Series B (JRSSB) (1), 
Journal of the Royal Statistical Society Series C (JRSSC) (1), Sankhya A (2), Scientific Reports (1), Spatial Statistics (4), Statistica Sinica (3), Statistical Computing (2), Statistics in Medicine (2).
\mylift{-1.7em}
\subsection*{Honors and Awards}
\vskip -2mm \noindent \textbf{Research:} 
\mydot{-0.1em}
\item \vskip -4mm Honorable mention: Lindley Prize, International Society
for Bayesian Analysis (ISBA) (2020).
\item Honorable mention: Savage Award (Applied Methodology), International Society
for Bayesian Analysis (ISBA) (2018).
\item ASA Outstanding Statistical Application Award, American Statistical
Association (2017).
\item ENAR Distinguished Student Paper Award, International Biometric Society,
Austin, TX (2016).
\item Delta Omega Honorary Society Student Inductee (Pi Chapter), Minneapolis,
MN (2016).
\item Best Student Seminar Presentation Award, Division of Biostatistics, University
of Minnesota, Minneapolis, MN (2016).
\item Inter-disciplinary Doctoral Fellowship 2015-16, Division of Biostatistics, University
of Minnesota Graduate School, Minneapolis, MN (2015).
\item JSM Student Paper Award, American Statistical Association, Section on
Bayesian Statistical Science, Boston, MA (2014).
Also selected for best paper award in Statistics and the Environment Section
\item Best Paper Award, Division of Biostatistics, University of Minnesota, Minneapolis,
MN (2014).
\vskip 1mm \noindent \textbf{Teaching, Advising, and Mentoring:} \vskip -3mm
\item 2019-2020 JHU AMTRA Award (Advising, Mentoring, \& Teaching Recognition) by JHSPH Student Assembly (2020)
\item Excellence in Teaching, Johns Hopkins Bloomberg School of Public Health,
Fourth Quarter, Probability IV (2018).
\item Outstanding Teaching Assistant Award, Division of Biostatistics, University of
Minnesota, Minneapolis, MN (2014).
\vskip 1mm \noindent  \textbf{Peer review:} 
\item Top 1\% of reviewers in Mathematics, Publons (2018)
\item Top 1\% of reviewers in Mathematics, Publons (2017)\\
%\vskip 1mm \noindent  \textbf{Conference Travel Awards:} 
%\item ISBA World Meeting, International Society for Bayesian Analysis, Edinburgh, UK (2018).
%\item G70 Conference, Duke University, Durham, NC (2015).
%\item ISBA World Meeting, International Society for Bayesian Analysis, Cancun,
%Mexico (2014).
%\item Conference on Non-parametric Statistics for Big Data and Celebration to Honor
%Professor Grace Wahba, University of Wisconsin, Madison, WI (2014).
%\item Pan-American Advanced Study Institute on Spatio-Temporal Statistics, Travel
%grant from National Science Foundation, Buzios, Brazil (2014).
\ee
\mylift{-2.5em}
\subsection*{PUBLICATIONS \ {\small \em  The white numbers in black boxes indicate first  author (including equal contributions) or senior author manuscripts, * indicates a mentored student or post-doctoral fellow of Dr. Datta; $^\dag$ indicates equal contributions.}}

\subsection*{Articles (Published, In press, Minor revisions)}

\myben{0.4em}
\mine *Fiksel J, Zeger S, \textbf{Datta A} (2021) {\dg A Transformation-free Linear Regression for Compositional Outcomes and Predictors} {\it Biometrics (In press)}
\mine *Fiksel J, \textbf{Datta A}, Amouzou A, Zeger S. (2021) {\dg Generalized Bayes Quantification Learning under Dataset Shift } {\it  Journal of the American Statistical Association Theory and Methods (In press)}
\mine \textbf{Datta, A,} *Saha, A, Levy-Zamora, M, Buehler, Colby, Hao, L, Xiong, F, Gentner DR, Koehler K (2020) {\dg Statistical field calibration of a low-cost PM2.5 monitoring network in Baltimore} {\it Atmospheric Environment 242,
	117761,
ISSN 1352-2310}
\item Finley AO, \textbf{Datta A}, Banerjee S. (2020) {\dg spNNGP R package for Nearest Neighbor Gaussian Process models} {\it Journal of Statistical Software (Accepted)}
\mine \textbf{Datta A}, *Pita, A, Rao, A, Sithole, B, Mnisi, Z, and Baral, S. (2020)	{\dg Size Estimation of Key Populations in the HIV Epidemic in eSwatini using incomplete and misaligned capture-recapture data} {\it Annals of Applied Statistics, 14(3), 1207--1241 }
\mine \textbf{Datta A}, *Fiksel J, Amouzou A, Zeger S. (2020) {\dg Regularized Bayesian transfer learning for population level etiological
	distributions} {\it Biostatistics, ISSN 1465--4644}
\mine \textbf{Datta A}, Zou H. (2019) {\dg A note on cross-validation for Lasso under measurement
	errors} {\it Technometrics, 62(4), 549--556 }
\mine \textbf{Datta A}, Banerjee S, Hodges JS., Gao, L. (2019)  {\dg Spatial disease mapping using
		Directed Acyclic Graph Auto-Regressive (DAGAR) models} {\it Bayesian Analysis 14(4), 1221--1244}
	\item Gao, L., \textbf{Datta A}, Banerjee S, (2020) {\dg Spatial Modeling for Correlated Cancers Using Bivariate Directed Graphs} {\it Annals of Cancer Epidemiology 	4, ISSN 2616-4213}
\item Flores-Moreno H, Fazayeli F, Banerjee A, \textbf{Datta A}, Kattge J, Butler EE, Atkin O,
Wythers K, Chen M, Anand M, Bahn M, Burrascano S, Byun C, Cornelissen J,
Craine J, Gonzalez-Melo A, Hattingh W, Jansen S, Kraft N, Kramer K, Laughlin 
D, Minden V, Niinemets U, Onipchenko V, Penuelas J, Soudzilovskaia N, Reich 
PB. (2019) {\dg Robustness of trait connections between multiple plant organs across
	environmental gradients, growth forms} {\it Global Ecology and Biogeography 28(12), 1806--1826}
\item Taylor-Rodriguez D, Finley AO, \textbf{Datta A}, Babcock C, Andersen H, Cook BD,
Morton DC, Banerjee S. (2019)
{\dg Spatial Factor Models for High-Dimensional, Large Spatial Data: An Application in Forest Variable Mapping}
{\it Statistica Sinica 26(29) 1155--1180}
\item Zhang L, \textbf{Datta A}, Banerjee S. (2019) {\dg Practical Bayesian Inference for Massive Spatial Data on Modest Computing Environments}
{\it Statistical Analysis and Data Mining: The ASA Data Science Journal 12.3:197-209.}
\item Finley AO, \textbf{Datta A}, Cook BC, Morton DC, Andersen HE, Banerjee S. (2019)
{\dg Efficient algorithms for Bayesian Nearest Neighbor Gaussian Processes}
{\it  Journal of Computational and Graphical Statistics 1-14.}
\item  Heaton MJ, \textbf{Datta A}, Finley AO, Furrer R, Guhaniyogi R, Gerber F, Gramacy RB, Hammerling D, Katzfuss M, Lindgren F, Nychka DW, Sun F, Zammit-Mangion A. (2019)
{\dg A Case Study Competition Among Methods for Analyzing Large Spatial Data}
{\it Journal of Agricultural, Biological and Environmental Statistics 24(3) 398--425.}
\begin{itemize}
	\item Best Paper award for 2018-2019 in the Journal of Agricultural, Biological and Environmental Statistics by the International Biometric Society
\end{itemize}
\mine \textbf{Datta A}, Lin W, Rao A, Diouf D, Kouame A, Edwards JK, Bao L, Louis TA, Baral SB (2019)
{\dg Bayesian estimation of MSM population in Côte d’Ivoire}
{\it  Statistics and Public Policy 6(1), 1-13.}
\mine \textbf{Datta A}, Zou H, Banerjee S. (2019)
{\dg Bayesian high-dimensional regression for change point analysis}
{\it  Statistics and Its Interface 12(2), 253-264.}
\item Edwards JK, Hileman S, Donastorg Y, Sanchez R, Zadrozny S, Baral SB, Hargreaves 
J, Fearon E, Zhao J, \textbf{Datta A}, Weir SS. (2018)
 {\dg Estimating sizes of key populations at the national level: considerations for study design, analysis}
{\it  Epidemiology 29(6): 795–803}
\mine *Saha A, \textbf{Datta A.} (2018)
{\dg BRISC: Bootstrap for rapid inference on spatial covariances}
{\it Stat e184}
\begin{itemize}
	\item \vskip -2mm American Statistical Association Section on Statistical Computing Student paper award for A. Saha at Joint Statistical Meetings, 2018.
	\item One of two papers selected for `Highlights of the Stat journal' session at International Statistical Institute World Congress, 2019. 
\end{itemize}
\mine \textbf{Datta A}, Zou H. (2017) 
{\dg CoCoLasso for High-dimensional Error-in-variables Regression}
{\it Annals of Statistics 45(6): 2400-2426}
\mine $^\dag$ Butler EE, $^\dag$ \textbf{Datta A.} / $\cdots$ 48 authors $\cdots$ / Reich, PB. (2017)
{\dg Mapping local and global variability in plant trait distributions}
{\it  Proceedings of the National Academy of Sciences 114(51): E10937–E10946}
\mine \textbf{Datta A}, Banerjee S, Finley AO, Hamm NAS, Schaap M. (2016) {\dg Non-separable
	Dynamic Nearest Neighbor Gaussian Process Models for Large Spatio-temporal Data with
	Application to Particulate Matter Analysis}
{\it  Annals of Applied Statistics 10(3): 
	1286-1316}
\begin{itemize}
	\item \vskip -2mm American Statistical Association Outstanding Statistical Application award (2017).
	\item Eastern North American Region (ENAR) distinguished student paper award for A. Datta (2016). 
\end{itemize}
\mine \textbf{Datta A}, Banerjee S, Finley AO, Gelfand AE. (2016)
{\dg On nearest-neighbor Gaussian
	process models for massive spatial data}
{\it  Wiley Interdisciplinary Reviews: Computational
	Statistics 8(5) 162-171}
\mine \textbf{Datta A}, Banerjee S, Finley AO, Gelfand AE. (2016) 
{\dg Hierarchical Nearest Neighbor
	Gaussian Process models for Large Geostatistical Datasets} 
{\it Journal of the American
	Statistical Association Theory and Methods 111(514) 800-812}
\begin{itemize}
	\item One of top 5 most cited papers in the Journal of the American Statistical Association between 2016-2020.
	\item \vskip -2mm American Statistical Association Section on Bayesian Statistics (SBSS) student paper award (2014) for A. Datta. 
\end{itemize}
\ee

\subsection*{Manuscripts Submitted}
\mycon{0.4em}
\mine *Saha A, Basu S, \textbf{Datta A} {\dg GLS-style Random forests for spatially dependent data} {\it Under Major Revision at the Journal of the American Statistical Association Theory and Methods}
%\mine *Fiksel J, Zeger S, \textbf{Datta A} {\dg A Transformation-free Linear Regression for Compositional Outcomes and Predictors} {\it Under Revision at Biometrics}
\mine *Dey D, \textbf{Datta A}, Banerjee S {\dg Graphical Gaussian Processes for highly multivariate spatial data}
\begin{itemize}
	\item \vskip -2mm American Statistical Association Section on Bayesian Statistics (SBSS) student paper award (2020) for D. Dey.
\end{itemize}
\item Wang G, \textbf{Datta A}, Lindquist M {\dg Bayesian Functional Registration of fMRI Data} 
\mine \textbf{Datta A} {\dg Sparse Cholesky matrices in spatial statistics}
\item Gao, L., \textbf{Datta, A.}, Banerjee, S. {\dg Hierarchical Multivariate Directed Acyclic Graph Auto-Regressive (MDAGAR) models for spatial diseases mapping}
\item Wythers KR, Butler EE, Flores-Moreno, H, Chen M, \textbf{Datta A}, Ricciuto DE, Atkin OK, Kattge J, Thorton PM, Banerjee A, Reich PB {\dg Improved logic and parameterization of maintenance respiration alter seasonal and spatial carbon cycling output from a global land surface model}
\item Butler EE, Wythers KR, Flores-Moreno, H, Ricciuto DM, \textbf{Datta A}, Banerjee A, Atkin OK, Kattge J, Thorton PE, Mathur A, Burrascano S, Byun JHC, Forey E, Jansen S, Kramer K, Minden V, and Reich PB {\dg The influence of functional diversity on terrestrial carbon uptake}
\ee

%\subsection*{PRACTICE ACTIVITIES}
\mylift{-1.5em}
\subsection*{Software}

\myben{0.4em}

\item
BRISC (2018) ($13870$ CRAN downloads as of Feb, 2021)
%BRISC is an R-package on CRAN for rapid estimation, prediction and inference for large spatial data in a frequentist setup. BRISC estimation and prediction relies on nearest neighbor approximations of the spatial Gaussian Process likelihood, and uses a scalable paramteric bootstrap to provide inference for all spatial parameters. To our knowledge, currently BRISC is the only R-package that provides confidence intervals in a frequentist setup for all parameters including the spatial variance and range of Gaussian Process. Inference from BRISC is highly competitive with those obtained on Bayesian approaches relying on MCMC, while being manifold times faster.
\item
calibratedVA (2018) (Github download stats not available)%$\blacktriangleright$
%calibatedVA is an R-package on Github for local calibration of national and sub-national cause specific mortality (CSMF) estimates produced by algortihms based on verbal autopsy data. These computer coded verbal autopsy (CCVA) algorithms usually rely on non-local gold standard training data and can be inaccurate in a local context. calibratedVA uses the output of the CCVA algorithm and limited amount of local gold standard data to update the CSMF estimates using a fast Bayesian hierarchical model. calibratedVA also has an ensemble calibration option where outputs from multiple CCVA algorithms are used to produce an unified calibrated CSMF estimate. the package can also be used in other general contexts to calibrate any discrete classifier (or a set of classifiers) based on limited local labeled data.
\item 
spNNGP (2017) ($14728$ CRAN downloads as of Feb, 2021)%$\blacktriangleright$
%spNNGP is an R package on CRAN for fully Bayesian analysis of massive spatial data. Spatial analysis of point process data is usually computationally expensive requiring memory and computations that are quadratic and cubic in the number of locations where data is observed. spNNGP implements a class of scalable Nearest Neighbor Gaussian Process models that uses memory and computations that are linear in the size of the data. spNNGP enables fast fully Bayesian inference of all parameters and proper uncertainty quantified predictions at new locations. An MCMC-free hybrid Bayesian conjugate NNGP is also included which is super fast even for spatial datasets with millions of locations. The new version of spNNGP also has the option to run Bayesian spatial GLM for binary spatial data using Nearest Neighbor Gaussian Processes. 
\item 
codalm (2020) ($4063$ CRAN downloads as of Feb, 2021) %$\blacktriangleright$
%codalm is an R-package for linear modeling of compositional data (coda). It implements a simple  transformation-free regression of a compositional outcome on a compositional prediction using an M-estimation method. Estimates of the regression-coefficient matrix, bootstrap-based confidence intervals are provided. A permutation based test of linear association is also offered.

\item
RandomForestsGLS (2021) ($911$ CRAN downloads as of Feb, 2021)
%RandomForestsGLS is an R-package for fitting non-linear regression models on dependent data (spatial and temporal) with Generalised Least Square (GLS) based Random Forests (RF-GLS) detailed in Saha, Basu and Datta (2020). For spatial data, `RandomForestsGLS` combines the strengths of Random Forest and Gaussian Process to estimate and predict non-linear functions using nearest neighbor Gaussian Process. For time-series data, `RandomForestsGLS` uses the AR (auto-regressive) process covariance structure with Random Forests for estimation. 
\ee

%\subsection*{TEACHING}
\mylift{-1.5em}
\subsection*{PhD Advisees}

\myben{-0.1em}
\item Saha, Arkajyoti, Doctor of Philosophy, Biostatistics (2016 -- present, co-advised with Nilanjan Chatterjee).
\item Dey, Debangan, Doctor of Philosophy, Biostatistics (2017 -- present, co-advised with Vadim Zipunnikov).
\item Gilbert, Brian, Doctor of Philosophy, Biostatistics (2019 -- present, co-advised with Betsy Ogburn).
\item Heffernan, Claire, Doctor of Philosophy, Biostatistics (2019 -- present)
\item Fiksel, Jacob, Doctor of Philosophy, Biostatistics (2015 -- 2020).
\ee

\mylift{-1.5em}
\subsection*{ScM Advisees}
\myben{-0.1em}
\item Xiang, Chen, Master of Science, Biostatistics (2020 -- present)
\item Pita, Andrew, Master of Science, Biostatistics (2017 -- 2019)
\ee
\mylift{-1.5em}
%
%\subsection*{Academic Advisees}
%
%\myben{-0.1em}
%
%\item Kuo, Albert. Doctor of Philosophy, Biostatistics (2017 -- 2019).
%\item Fu, Martina. Doctor of Philosophy, Biostatistics (2019).
%
%\ee
%
%\mylift{-1.5em}
%
%\subsection*{Thesis Committees / Thesis Reader}
%
%\myben{-0.1em}
%
%\item \dn{Pita}, Andrew, Master of Science, Biostatistics (2019).
%\ee
%
%\mylift{-1.5em}
%
%\subsection*{Preliminary Oral Participation \ \tiny * committee chair}
%
%\myben{-0.1em}
%\item \dn{Gilbert}, Brian. Doctor of Philosophy, Biostatistics (2021, expected).
%\item \dn{Wang}, Guoqing. Doctor of Philosophy, Biostatistics (2020).
%\item \dn{Dey}, Debangan. Doctor of Philosophy, Biostatistics (2020).
%\item \dn{Saha}, Arkajyoti. Doctor of Philosophy, Biostatistics (2019).
%\item \dn{Windle}, Michael. Doctor of Philosophy, Epidemiology (2019).
%\item \dn{Kim}, Ji Soo. Doctor of Philosophy, Biostatistics (2019).
%\ee
%
%\mylift{-1.0em}
%
%\subsection*{Final Oral Participation \ \tiny * committee chair}
%
%\myben{-0.1em}
%\item \dn{Kim}, Ji Soo. Doctor of Philosophy, Biostatistics (2020).
%\item \dn{Fiksel}, Jacob, Doctor of Philosophy, Biostatistics (2020).
%\item \dn{Wang}, Craig. Doctor of Philosophy, University of Zurich, Department of Mathematics and Department of Computational Science (2019).
%\item \dn{Lee}, Youjin, Doctor of Philosophy, Biostatistics (2019).
%\item \dn{Colston}, Josh, Doctor of Philosophy, International Health (2018).
%\ee
%\mylift{-0.5em}

\subsection*{Classroom Instruction - Principal Instructor (JHSPH)}
\mydot{-0.1em}
\item 140.724 Probability Theory IV (2021, 2020, 2019, 2018).
\item 140.850 Biostatistics PhD Seminar on Advanced spatial statistics (2021, 2019, 2018). 
%\item 140.724 Probability Theory IV (4$^{th}$ term, 2020).
%\item 140.724 Probability Theory IV (4$^{th}$ term, 2019).
%\item Biostatistics PhD seminar (3$^{rd}$ term, 2019).
%\item 140.724 Probability Theory IV (4$^{th}$ term, 2018).
%\item 140.850 Advanced spatial statistics (3$^{rd}$ term, 2018).
\item 140.850 Scalable methods for large spatial data (2017).

\ee

%\mylift{-1.5em}
%
%\subsection*{Classroom Instruction - Invited Guest Lecturer (JHSPH)}
%
%\mydot{-0.1em}
%\item 140.651.01 Methods in Biostatistics I (2019)
%\item 340.680.01 Environmental and Occupational Epidemiology (2018).
%
%\ee

\mylift{-1.5em}

\subsection*{Short courses}

\mydot{-0.1em}

\mylift{-1.em} \item Full day short course on Bayesian models for high dimensional spatial data, Joint Statistical Meetings (2017). 

\ee


%\subsection*{Teaching Assistant}
%\vskip -2mm {\em Division of Biostatistics, University of Minnesota} 
%
%\mydot{-0.1em}
%
%\item Advanced Statistical Inference, Instructors: Dr. Cavan Reilly and Dr. David Vock, Spring 2015
%
%\item Probability Models for Biostatistics, Instructor: Dr. Baolin Wu, Fall 2014
%
%\item Bayes Decision Theory and Data Analysis, Instructor: Dr. Sudipto Banerjee, Spring 2014
%
%\item Advanced Statistical Inference, Instructors: Dr. Julian Wolfson and Dr. David Vock, Spring 2014
%
%\item Probability Models for Biostatistics, Instructor: Dr. Baolin Wu, Fall 2013
%
%\item Advanced Regression, Instructor: John Hughes, Ph.D, Spring 2012
%
%\item Statistical Methods for Correlated Data, Instructor: Dr. Julian Wolfson, Fall 2012

%\ee
\mylift{-1.em}
\subsection*{Research Grants as Principal  Investigator}  

\mydot{0.3em}

\item[$\bullet$]
{\it \textbf{Highly multivariate geo-statistics using graphical models (NSF DMS-1915803)}}\\[0.0em]
\dn{Dates:} July 2019 to June 2022.\\
\dn{Principal Investigators:} Abhirup Datta.\\
\dn{Responsibility:} Principal Investigator.

\item[$\bullet$]
{\it \textbf{Statistical Maps of Air Quality in Baltimore City Using Low-Cost Monitoring Data (Bloomberg American Health Initiative Spark Award)}}\\[0.0em]
\dn{Dates:} July 2018 to June 2019.\\
\dn{Principal Investigators:} Abhirup Datta and Kirsten Koehler.\\
\dn{Responsibility:} Principal Investigator.

\ee

\end{document}


